Untitled

### 2022-11-04 Task_2_draft.Rmd
adding comments in code

```{r}
#Creating function for algorithm
Fisher.scoring.alg <- function(X,y){
  #Setting initial guess of beta coefficients
  beta.new <- matrix(c(1,1),nrow=2,ncol=1)
  #Setting objects for conditions of when stop iterations (while loop)
  flag <- 1
  eps <- 0.00001
  c <- 0
  max.iter <- 100000000

@@

    #Checking for convergence
    if (abs(sum(beta.new)-sum(beta))<eps){
      flag <- 0
    }
    c <- c+1
  }
  #Variance covariance matrix
  var.cov.mat <- solve(t(X)%*%X)

  return("estimates"=beta.new)
}

@@

>>>>

```{r}
#Creating function for algorithm
Fisher.scoring.alg <- function(X,y){
  #Setting initial guess of beta coefficients

  beta.new <- matrix(c(0,1),nrow=2,ncol=1)
  #Setting objects for conditions of when stop iterations (while loop)
  flag <- 1
  #setting size of absolute difference between beta iterations when convergence is reached
  eps <- 0.0000001
  #Setting loop counter
  c <- 0
  #Max iterations before 
  max.iter <- 1000000

@@

    #Checking for convergence
    if (abs(sum(beta.new)-sum(beta))<eps){
      flag <- 0
    }

    if (c>max.iter){
      stop("Max number of iterations reached: Non-convergence of beta")
    }
    c <- c+1
  }
  #Variance covariance matrix
  var.cov.mat <- solve(t(X)%*%X)

  return(beta.new)
}

@@

```{r}
#Finding var-cov matrix

t(X)%*%(X)
```
